---
title: "Coursera Shiny Project"
author: "Elena Y"
date: "31 March 2019"
output:
  
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, comment = "")
```

## Overview

For the main application please visit https://elenay.shinyapps.io/MyShinyProject/.

- The application uses _mtcars_ dataset The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).
- The interactive shiny application allows exploring the relationship between the weight of the vehicle and miles per gallon. 
- The user can choose to visualise only subset of results selecting the range of vehicle weight

## Web Application - user instructions
The developed shiny application visualize the relationship between the car weight and miles per gallon for selected car brands with different number of cylinders. The application enables users

- to select the range of car weight and re-plotting the chart using the range slider
- to select a subset of cars with specific number of cylinders (4, 6 or 8) using the input boxes and investigate how the relationship between car weight and mpg changes by the number of cylinders. 
- the results are visualised as a scatter plot with each data point clearly labelle with car brand name.  

## Dataset Summary
Car brands analyzed
```{r datasum}
#suppressWarnings(library(plotly)) 
row.names(mtcars)
```
mpg - miles per gallon, wt - weight, cyl - cylinders
```{r datasummary1}
mtcars2 <- mtcars[,c("mpg","wt","cyl")]
str(mtcars2)
```
wt:
```{r datasummary2}
summary(mtcars$wt)
```
cyl:
```{r datasummary3}
summary(mtcars$cyl)
```

## Car Weight vs Miles per Gallon by the Number of Cylinders 
```{r plot1}
suppressWarnings(library(ggplot2)) 
ggplot(mtcars, aes(x=wt, y=mpg, fill=cyl)) +
  theme(panel.background = element_rect(fill = NA),
        panel.grid.minor = element_line(color = NA),
        panel.grid.major.x = element_line(color = NA),
        panel.grid.major.y = element_line(color = "grey95"),
        panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.title = element_text(hjust = 0.5),
        text = element_text(size = 10, color = "black", face = "bold"),
        plot.caption = element_text(hjust = 0.5)) + 
  geom_point(size=2) +
  geom_label(label=rownames(mtcars), color="white", size=3) + 
  scale_shape_manual(values = c(1,16)) +
  labs(y = "Miles per Gallon",
       x = "Car weight in 000s pounds",
       title = "Car weight vs MPG by car cylinders")
```


